A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-05-20 main.tex
Updates from Overleaf

\documentclass[conference]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

% correct bad hyphenation here

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{algpseudocode}

\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}

% \newcommand{\cm}[1]{#1}
\newcommand{\mr}[1]{\textit{{\color{red}#1}}}
\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{A Cloud Native Approach to Adversarial Robustness of Neural Networks}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
cmeyers@cs.umu.se}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
\IEEEauthorblockA{\textit{Elastisys} \\
% \textit{Umeå University}\\
% Lund, Sweden \\
mohammad.saleh@elastisys.com}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
tommy@cs.umu.se}
\and
\IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
elmroth@cs.umu.se}
}

@@

\begin{abstract}
\cm{Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model a run-time, evaluating the robustness of models to these evasion attacks is of critical importance.}
Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
\cm{In this paper, we use survival analysis to present a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.}
For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, \cm{so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data. However, in practice, this means that each model configuration needs to be evaluated against real-world deployment samples which can be prohibitively expensive or time-consuming to collect --- especially when other parts of the software or hardware stack are developed in parallel.} To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, test-set accuracy by using adversarial attacks to induce failures on a reference model architecture before deploying the model to the real world. We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. This provides a way to evaluate the model and optimize it in a single step, while simultaneously allowing us to model the effect of model parameters on training time, prediction time, and accuracy. Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
\end{abstract}

@@

Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. 
\cm{Statistical learning theory \cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters. To overcome this, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has  yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. We also know that  reaching safety-critical standards using test-set accuracy would require an infeasibly large test set \cite{meyers}. Therefore, we propose using AFR models to simulate edge-cases and verify models using a small number of samples.}

\cm{Modern neural networks are massive--- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}}.
One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. One version of this open-source large language model (LLM) was able to outperform the commercially available GPT-3.5 model~\cite{liu2023goat} with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU), suggesting that consumer-level hardware can be used to effectively train large models in a reasonable time. Furthermore, popular models like Generative Pre-trained Transformer (GPT)~\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions or billions of parameters, requiring infeasibly large training datasets to verify a model\cite{vcdimension}. Media reports place the cost of training a GPT3 somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. \cm{While the benefits of a more portable model are plentiful, there is not yet a method for formalizing the relationship between cost and model performance. We present training and validation methodology with a focus on compute- and time-efficiency.}

Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for \cm{assessing model generalization}~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be in the range $[10^{-12}, 10^{-15}]$ depending on the number of lives at risk~\cite{iso26262}. Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern \cm{since inducing a failure at run-time has consistently shown to be trivial}~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}. Collecting, labelling, and testing a new set of data for every software change --- as required by law in most of the world~\cite{IEC61508,iso26262,aviation_software,safetyframework} --- would be prohibitively expensive. Therefore, a new evaluation methodology is required.

@@

\cm{In this paper, we use accelerated methods to predict model performance as a function of various model parameters. The methodology outlined in Sec.~\ref{afr} allows the model-builder to minimize the training cost, optimize for adversarial robustness, estimate the partial effects of covariates on model performance during routine training procedures, and perform a cost analysis (Sec.~\ref{cost}). We then demonstrate the efficacy of this methodology in Sec.~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Sec.~\ref{experiments}.}

\subsection{Contributions}
To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective \cm{methodology and software framework for the training (see: Sec.~\ref{afr}) and evaluation (see: Sec.~\ref{cost}) of machine learning models} that:
\begin{itemize}
    \item Optimizes for benign and adversarial accuracy simultaneously,
    \item Extends survival analysis to the realm of neural networks, 
    \item Demonstrates a scalable and effective method that trains a model while simultaneously estimating the asymptotic effect of various hyperparameters, and
    \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.   
\end{itemize}

\cm{Sec.~\ref{background} defines terms used throughout the paper. Sec.~\ref{afr} outlines the training and evaluation methodology presented in this paper.  Section ~\ref{cost} outlines the resulting cost analysis framework, arising from the methodology in the previous section. Sec.~\ref{experiments} outlines the software components and specific experiments that were conducted, while Sec.~\ref{results} contains the results and discussions of those experiments. Sec.~\ref{considerations} and Sec.~\ref{conclusion} reveal the caveats and the conclusions respectively.}

@@

ML pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises. The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference. Efficiently orchestrating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.

A \textit{service} is the smallest component of a ``cloud-native" software stack. In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. A service \textit{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between services in a distributed system. It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services.

A service \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the services within the system. These components facilitate various capabilities and functionalities essential for managing the communication between services. Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures. \cm{For ML applications, these services are often divided into ``training" and ``inference" configurations that often distinct hardware and software configurations~\cite{wang2019benchmarking}. In this work, we leveraged Kubernetes to manage a multi-stage ML pipeline.}

@@

Choosing the correct learning rate is critical for model performance --- greatly effecting both the accuracy and the run-time requirements. A small learning rate will will more closely follow the true gradient of a class boundary~\cite{cao2019generalization}, but will converge slower, all other things being equal. Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data, \textit{etc}~\cite{granziol2022learning}. Graphics cards with larger amounts of RAM are able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch. A ``good" learning rate will allow a model converge quickly~\cite{smith2019super,granziol2022learning} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, scale, and bit depth of the data. However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}. Furthermore, since hardware is typically billed by the hour on public clouds, so optimizing the training and inference times allows a model-builder to minimize the cost of deployment.

@@

We propose a methodology for model training and verification using accelerated failure rate (AFR) models, drawn from the field of \textit{survival analysis}. \cm{Additionally, since one of our goals is a cost-effective model evaluation technique, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.}
AFR models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. \cm{In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components. This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.}
\cm{The section below outlines our methodology for modelling the effect of model hyper-parameters during routine training procedures. In this section, we precisely outline the methodology for using survival analysis during the training of machine learning algorithms. We provide a formal algorithm in Fig.~\ref{fig:alg} and a visual diagram in ~\ref{fig:experiments}.}

\cm{In the subsections below, we define accuracy (Sec.~\ref{acc}) and failure rate (Sec.~\ref{failure_rate})  in the context of survival analysis to provide a pedagogical definition of survival time (Sec.~\ref{survival_time}). We then discuss the importance of the ``acceleration assumption" (Sec.~\ref{accelerated}), the optimization algorithm (Sec.~\ref{optimisation}), and the advantages of this approach (Sec.~\ref{advantages}).}

\begin{figure}[h!]
    \caption{\textbf{Algorithm: }Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x$ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and a number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, e.g. $N_t$ is size of the training set.
    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
    \State \textbf{Optimise $\theta$:} over $x_t$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
    \State \textbf{Record:} $T_t[i] \gets$ Training Time.
    \State \textbf{Infer:}  $ \hat{y_i} = K(x_i, \theta) $.
    \State \textbf{Record:}  $ T_i[i] \gets $  Inference Time.
    \State \textbf{Calculate:}  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}.
    \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
    \State \textbf{Infer:}  $ y' = K(x_a, \theta) $.
    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc})
    \EndWhile
    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates, $N_a$ is the attack size array.
    \State \textbf{Return:} $S_{\theta}$
\end{algorithmic}
\end{figure}

@@

\subsection{Accuracy}
\label{acc}
 It measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures. Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data. The benign accuracy, $\lambda_{ben}$, is defined as
\begin{equation}
    \lambda:= \mathrm{Accuracy} := 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}},
    \label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. In addition, it ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}. Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}. \cm{We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test set $\lambda_{adv}$ to denote the accuracy on the adversarial examples.}

\subsection{Failure Rate}
\label{failure_rate}
The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}. To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, \cm{such that the failure rate is}
\[
    h_{ \theta}(t) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t} t,
\]
where $\mathbb{P}(\textrm{False~Classification})$ is the probability of a false classification, $\Delta t$ is a time interval, and $t$ is a point in time. \cm{Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$. By reparameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure rate model.}

\subsection{AFR Models}
\label{survival_time}
\cm{Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For machine learning, this means inducing failures during training to measure generalization performance.}

>>>>

\documentclass[journal]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

% correct bad hyphenation here
\usepackage[maxcitenames=3,natbib=true,giveninits=true]{biblatex}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{algpseudocode}

% \newcommand{\cm}[1]{\textit{{\color{blue}#1}}}

\newcommand{\cm}[1]{#1}
\newcommand{\mr}[1]{\textit{{\color{red}#1}}}
\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{A Cloud Native Approach to Adversarial Robustness of Neural Networks}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% cmeyers@cs.umu.se}
% \and
% \IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
% \IEEEauthorblockA{\textit{Elastisys} \\
% % \textit{Umeå University}\\
% % Lund, Sweden \\
% mohammad.saleh@elastisys.com}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% tommy@cs.umu.se}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% elmroth@cs.umu.se}
% }

@@

\begin{abstract}
Considering the growing prominence of production-level AI and the threat of adversarial attacks that can evade a model a run-time, evaluating the robustness of models to these evasion attacks is of critical importance.
Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem that reduces development speed, increases cost of development, and makes it difficult (if not impossible) to parse cause from effect.
In this paper, we use survival analysis to present a cloud-native, time-efficient and precise method for predicting model performance in the presence of adversarial noise.
For neural networks in particular, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex, so researchers generally rely on benchmark datasets to assess the ability of a model to generalize beyond the training data. However, in practice, this means that each model configuration needs to be evaluated against real-world deployment samples which can be prohibitively expensive or time-consuming to collect --- especially when other parts of the software or hardware stack are developed in parallel. To address this, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, test-set accuracy by using adversarial attacks to induce failures on a reference model architecture before deploying the model to the real world. We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. This provides a way to evaluate the model and optimise it in a single step, while simultaneously allowing us to model the effect of model parameters on training time, prediction time, and accuracy. Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
\end{abstract}

@@

Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. 
Statistical learning theory \cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters. To overcome this, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has  yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. We also know that  reaching safety-critical standards using test-set accuracy would require an infeasibly large test set \cite{meyers}. Therefore, we propose using accelerated failure time models to simulate edge-cases and verify models using a small number of samples.

Modern neural networks are massive--- they have have grown to be one of the largest consumers of data-center power, especially with the rise of generative AI~\cite{msft_water}.
One of Facebook's large language models, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. One version of this open-source large language model (LLM) was able to outperform the commercially available GPT-3.5 model~\cite{liu2023goat} with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU), suggesting that consumer-level hardware can be used to effectively train large models in a reasonable time. Furthermore, popular models like Generative Pre-trained Transformer (GPT)~\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions or billions of parameters, requiring infeasibly large training datasets to verify a model\cite{vcdimension}. Media reports place the cost of training a GPT3 somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. While the benefits of a more portable model are plentiful, there is not yet a method for formalizing the relationship between cost and model performance.

Furthermore, even if we ignore the immense cost of training modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for assessing model generalization~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be in the range $[10^{-12}, 10^{-15}]$ depending on the number of lives at risk. Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern since inducing a failure at run-time has consistently shown to be trivial~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}. Collecting, labelling, and testing a new set of data for every software change --- as required by law in most of the world~\cite{IEC61508,iso26262,aviation_software,safetyframework} --- would be prohibitively expensive. Therefore, a new evaluation methodology is required.

@@

In this paper, we use accelerated methods to predict model performance as a function of various model parameters. The methodology outlined in Sec.~\ref{afr} allows the model-builder to minimize the training cost, optimise for adversarial robustness, estimate the partial effects of covariates on model performance during routine training procedures. Then, one can perform a cost analysis (Sec.~\ref{cost}). We then demonstrate the efficacy of this methodology in Sec.~\ref{results} by examining the role of hardware on model performance, the particulars of which are outlined in Sec.~\ref{experiments}.

\subsection{Contributions}
To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see: Figs.~\ref{fig:alg}\&~\ref{fig:experiments}) and software framework (see: Fig.~\ref{fig:architecture}) for the training (see: Sec.~\ref{afr}) and evaluation (see: Sec.~\ref{cost}) of machine learning models that:
\begin{itemize}
    \item optimises for benign and adversarial accuracy simultaneously,
    \item Extends survival analysis to the realm of neural networks, 
    \item Demonstrates a scalable and effective method that trains a model while simultaneously estimating the asymptotic effect of various hyperparameters, and
    \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.   
\end{itemize}

Sec.~\ref{background} defines terms used throughout the paper. Sec.~\ref{afr} outlines the training and evaluation methodology presented in this paper.  Section ~\ref{cost} outlines the resulting cost analysis framework, arising from the methodology in the previous section. Sec.~\ref{experiments} outlines the software components and specific experiments that were conducted, while Sec.~\ref{results} contains the results and discussions of those experiments. Sec.~\ref{considerations} and Sec.~\ref{conclusion} reveal the caveats and the conclusions respectively.

@@

ML pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises. The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, attack generation, and inference. Efficiently orchestrating  and evaluating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.

One popular solution is using a network of interconnected services \cite{panchal2024reusable,hasselbring2017microservice,zhong2022machine,singh2023load}. A \textit{service} is the smallest component of a ``cloud-native" software stack. In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. 
A service \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the services within the system.  These components facilitate various capabilities and functionalities essential for managing the communication between services. Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures using a service mesh. For ML applications, these services are often divided into ``training" and ``inference" configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}. In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see: Fig.~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see: Fig.~\ref{fig:architecture}) across a variety of different hardware architectures (see: Tab.~\ref{tab:hardware}).

@@

Choosing the correct learning rate is critical for model performance --- greatly effecting both the accuracy and the training cost. A small learning rate will will more closely follow the true gradient of a class boundary~\cite{cao2019generalization}, but will converge slower, all other things being equal. Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data, \textit{etc}~\cite{granziol2022learning}. Graphics cards with larger amounts of RAM are able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch. A ``good" learning rate will allow a model converge quickly~\cite{smith2019super,granziol2022learning} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, scale, and bit depth of the data. However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}. Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.

@@

We propose a methodology for model training and verification using accelerated failure rate (AFR) models, drawn from the field of \textit{survival analysis}. Additionally, since one goal is cost-efficiency, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.
AFR models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components. This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
The section below outlines our methodology for modelling the effect of model hyper-parameters during routine training procedures. In this section, we precisely outline the methodology for using survival analysis during the training of machine learning algorithms. First, we provide a formal algorithm in Fig.~\ref{fig:alg} and a visual diagram in ~\ref{fig:experiments}. Then, in  the subsections below, we define accuracy (Sec.~\ref{acc}) and failure rate (Sec.~\ref{failure_rate})  in the context of survival analysis to provide a pedagogical definition of survival time (Sec.~\ref{survival_time}). We then discuss the importance of the ``acceleration assumption" (Sec.~\ref{accelerated}), the optimisation algorithm (Sec.~\ref{optimisation}), and the advantages of this approach (Sec.~\ref{advantages}).

\begin{figure}[h!]
    \caption{\textbf{Algorithm: }Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x$ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and a number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, e.g. $N_t$ is size of the training set.
    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
    \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
    \State \textbf{Record:} $T_t[i] \gets$ Training Time.
    \State \textbf{Infer:}  $ \hat{y_i} = K(x_i, \theta) $.
    \State \textbf{Record:}  $ T_i[i] \gets $  Inference Time.
    \State \textbf{Calculate:}  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}.
    \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
    \State \textbf{Infer:}  $ \hat{y}_a = K(x_a, \theta) $.
    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
    \EndWhile
    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
    \State \textbf{Return:} $S_{\theta}$
\end{algorithmic}
\end{figure}

@@

\subsection{Accuracy}
\label{acc}
  Accuracy measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures. Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data. The accuracy, $\lambda$, is defined as
\begin{equation}
    \lambda:= \mathrm{Accuracy} := 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}},
    \label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. In addition, it ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}. Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}. We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test set $\lambda_{adv}$ to denote the accuracy on the adversarial examples.

\subsection{Failure Rate}
\label{failure_rate}
The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}. To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, such that the failure rate is
\[
    h_{ \theta}(t) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t} t,
\]
where $\mathbb{P}(\textrm{False~Classification})$ is the probability of a false classification, $\Delta t$ is a time interval, and $t$ is a point in time. Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$. By re-parameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure rate model.

\subsection{AFR Models}
\label{survival_time}
Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For machine learning, this means inducing failures during training to measure generalization performance.
